---
title: "User analysis rtweet"
author: "Cherra"
date: "4 de abril de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("rtweet")
library("ggplot2")
library("dplyr")
library("lubridate")
library("purrr")
```

# Getting user

We will see the way of getting an user
```{r getUser}
user.name <- "joserraCasero"
tweets.user <- get_timelines(user.name, n = 1000)
tweets.user
```

## Some plotting

First of all we are going to see the tweeting frequency of that user


```{r}
tweets.user %>%
  ts_plot("7 days") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  labs(
    x = NULL, y = NULL,
    title = "Frequency of @joserraCasero from past 6 month",
    subtitle = "Twitter status (tweet) counts aggregated using 1 week intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```
### Getting people a user follow

```{r}
friends.id <- get_friends(user.name)
friends.object <-lookup_users(friends.id$user_id)
friends.object$screen_name
```

### Gettin user who follow an user

```{r}
followers.id <- get_followers(user.name)
followers.object <-lookup_users(followers.id$user_id)
followers.object$screen_name
```

# User operations

In this point I will play with followers and friends.
1. I'm getting people I follow and don't follow me
2. I'm getting people who follow me and I dont follow them


```{r}
fans <- anti_join(followers.id, friends.id)$user_id %>%
          lookup_users()
haters <- anti_join(friends.id, followers.id)$user_id %>%
          lookup_users()
mutuals <- inner_join(friends.id, followers.id)$user_id %>%
  lookup_users()


```



```{r last.tweet.hater}
haters.id <- select(haters, user_id)
last.tweet.hater <- get_timeline(haters.id[[1]], n = 1)
#last.tweet.hater <- get_timelines(haters, n = 1)
```

Once I have the last tweet of the follower who dont follow me, I'm going to filter them by who hasnt tweeted in one month


```{r filter user not active}
not.active.hater <- last.tweet.hater %>%
          filter(today() - as_date(last.tweet.hater$created_at) > 30)
not.active.hater$screen_name
```

